\begin{enumerate}
    \item Pure gold is 24 karats.
    \item One hour equals 60 minutes.
    \item The chemical symbol for iron is Fe.
    \item The femur is the longest bone in the human body.
    \item The golden ratio is approximately 1.61803.
    \item Earth’s seasons are caused by its axial tilt.
    \item Copper is an excellent conductor of electricity.
    \item A byte consists of 8 bits.
    \item Human red blood cells lack nuclei.
    \item There are 12 months in a year.
    \item A thermometer measures temperature.
    \item Fungi form a kingdom distinct from plants and animals.
    \item DNA is structured as a double helix.
    \item Avogadro’s number is about 6.022 $\times$ 10$^{23}$ per mole.
    \item At 25$^\circ$C, a neutral solution has pH 7.
    \item The chemical symbol for potassium is K.
    \item The chemical symbol for sodium is Na.
    \item Humans have 23 pairs of chromosomes.
    \item Diamond is an allotrope of carbon.
    \item The freezing point of mercury is about $-$38.83$^\circ$C.
    \item Ocean tides are primarily caused by the Moon’s gravity.
    \item In an isolated system, entropy tends to increase.
    \item A triangle cannot have two right angles in Euclidean geometry.
    \item The SI unit of energy is the joule.
    \item Table salt is sodium chloride.
    \item Marble is a metamorphic rock.
    \item The Eiffel Tower is located in Paris.
    \item The pH scale is logarithmic.
    \item Graphite conducts electricity.
    \item The skin is the body’s largest organ by area.
    \item Planck’s constant is about 6.626 $\times$ 10$^{-34}$ joule seconds.
    \item Zero is an even number.
    \item The speed of light in vacuum is 299,792,458 meters per second.
    \item Venus is the hottest planet in the Solar System.
    \item Room temperature is commonly about 20--25$^\circ$C.
    \item Strawberries are not true berries botanically.
    \item Basalt is a common volcanic rock.
    \item Jupiter is the largest planet in the Solar System.
    \item The ozone layer absorbs much of the Sun’s ultraviolet radiation.
    \item Bananas are botanically berries.
    \item The sinoatrial node is the heart’s natural pacemaker.
    \item Carbon 14 dating estimates the age of once living materials.
    \item The cheetah is the fastest land animal.
    \item The cerebrum is divided into two hemispheres.
    \item Giraffes and humans each have seven neck vertebrae.
    \item Tomatoes are fruits in botanical terms.
    \item A circle has 360 degrees.
    \item Africa is the second largest continent by area.
    \item Sleep includes REM and non REM stages.
    \item Photosynthesis converts carbon dioxide and water into glucose and oxygen.
\end{enumerate}